Week 3 Assignment

### 2018-09-11 DATA607/Week_3_Assignment.Rmd
Linted Week 3 Assignment for DATA 607

```{r}
library(stringr)
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

@@

```{r}
get_first_last <- function(n){
  # Strip out title and middle name
  n <- str_replace(n, '(Rev. )|(C. )|(Dr. )','')
  # Reorder if comma is present
  split_n <- unlist(str_split(n, ', '))
  if(length(split_n)==2){
    n <- paste(split_n[2],split_n[1])
  }
  return(n)
}

@@

```{r}
# Look for two letters followed by a period and a space
has_title <- str_count(name, '\\w{2}. ') > 1
has_title
```

@@

```{r}
# Find a space followed by one letter then a period then a space
has_second_name <- str_count(name, ' \\w{1}. ') == 1
has_second_name
```

>>>>

```{r}
library(stringr)
raw.data <- "555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

@@

```{r}
get_first_last <- function(n){
  # Strip out title and middle name
  n <- str_replace(n, "(Rev. )|(C. )|(Dr. )", "")
  # Reorder if comma is present
  split_n <- unlist(str_split(n, ", "))
  if (length(split_n) == 2){
    n <- paste(split_n[2], split_n[1])
  }
  return(n)
}

@@

```{r}
# Look for two letters followed by a period and a space
has_title <- str_count(name, "\\w{2}. ") > 1
has_title
```

@@

```{r}
# Find a space followed by one letter then a period then a space
has_second_name <- str_count(name, " \\w{1}. ") == 1
has_second_name
```
